### 2021-03-28 newvariant.tex
working on control

\section{Inferring relative strength from case data, in practice}

Seb Funk's analysis here.

\section{Intervention}

If $K(\tau)/L(\tau)$.

>>>>

\section{Implications for intervention strategies}

While the relative speed need not stay constant over the course of an epidemic, at any given point in epidemic, we can measure the speed of the new variant and the wild type and ask how much more intervention is required to control the spread of both strains (relative to measured conditions).
As a baseline scenario, we assume $\ry{wt}=0\,\textrm{/days}$ and $\delta=0.1\,\textrm{/days}$ (and therfore $\ry{var}=0\,\textrm{/days}$).
In this case, the wild type is already under control, whereas the variant requires additional intervention measures to stop growing.

Here, we consider two types of interventions:
a strength-like intervention which affects the kernel by a constant amount $\theta$ regardless of when they were infected ($K_{\mathrm{post}}(\tau) = K_{\mathrm{pre}}(\tau)/\theta$) and a speed-like intervention which affect the kernel at a constant rate $\phi$ ($K_{\mathrm{post}}(\tau) = K_{\mathrm{pre}}(\tau) \exp(-\phi \tau)$).
In this case, it is clear that we can control the spread of the variant when either $\theta > \Ry{var}$ or $\phi > \ry{var}$---these two quantities ($\theta$ and $\phi$) are also referred to as strength and speed of intervention, respectively.
In general, we can calculate the strength ($\theta = \Ry{pre}/\Ry{post}$) and speed ($\phi = \ry{pre} - \ry{post}$) of intervention, both providing equivalent measures for effectiveness of intervention, for any intervention by comparing epidemiological conditions before and after the intervention.
We compare how potential differences in generation-inteval distributions affect the control of the spread of the new variant using this strength-and-speed framework.
\swp{missing citation.}

\begin{figure}
\includegraphics[width=\textwidth]{control.pdf}
\caption{
\textbf{caption.}
}
\end{figure}
